\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-17 tex/paper.tex
Moved the JPF section

%\subsubsubsection{Perius}
%Perius is the name of the implementation that was made during this project. It is an anagram of
%Uprise and also a type of butterfly.

@@

@@

\newpage
\section{JPF}
\fix Not sure where to put this section

JPF was used to test the idea and state transitioning of the application. Its a very simplified
version of the real system that still contains all the important Copy-on-Write core concepts and the 
assumptions that have been made for the model. This simplified version could then be automatically
tested for soundness. It is not a proof that the model works, but it is very exhaustive in its
testing.

\subsection{Entities}
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{High Level Entity Relationships}
    \label{fig:relation}
\end{figure}

\subsubsection{Content}
Content is meta data about a file and is stored in a container, it is a form of virtual file.  The
content can refer to for example an image, video or binary blob.

\subsubsection{Project}
A project is what is created to contain all content and containers related to a real project. Files
can be changed within a project and the system can contain several projects and their virtual
content are completely disjoint.

\subsubsection{Container}
A container is a virtual folder within a project which can contain content and other containers.

\subsubsection{Snapshot}
A snapshot is a read-only container from the state which the container the was in when the snapshot
was created.  A snapshot can not be updated and can only be deleted from the root of the snapshot.
Snapshots are by default stored as siblings to the container which they were made from, but they can
be contained by any container.

\subsubsection{File}
A file refers to an actual physical file. Files are stored in the database to make backup,
deployment and migration easier.

\subsubsection{User}
A user is the structure that handles people who have been granted access to the system. Access to
the system is handled by a separate service, like LDAP.

\subsection{Execution}
Java path finder was used to show that the model and plan of how to build the system was sound. The
model was built in Java with the objective of being as reduced and simple as possible, without
loosing any of the cases that needed to be covered by the model checker. As the users are mainly
going to be handled by external systems they were not included in the model.

@@

\subsubsection{Front-end Refactor}
The application could be made substantially more efficient by rewriting the front-end to update
itself according to the REST response after a modification of the project tree, instead of 
re-fetching the full project tree every time a change is made.

>>>>

\subsubsubsection{Perius}
Perius is the name of the implementation that was made during this project. It is an anagram of
Uprise and also a type of butterfly.

@@

\subsection{JPF}
\fix Not sure where to put this section

JPF was used to test the idea and state transitioning of the application. It's a very simplified
version of the real system that still contains all the important Copy-on-Write core concepts and the 
assumptions that have been made in the model. This simplified version could then be automatically
tested for soundness. It is not a proof that the model works, but it is very exhaustive in its
testing.

\subsubsection{Entities}
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{High Level Entity Relationships}
    \label{fig:relation}
\end{figure}

\par \textbf{Content} \\
Content is meta data about a file and is stored in a container, it is a form of virtual file.  The
content can refer to for example an image, video or binary blob.\\

\par \textbf{Project} \\
A project is what is created to contain all content and containers related to a real project. Files
can be changed within a project and the system can contain several projects and their virtual
content are completely disjoint.\\

\par \textbf{Container} \\
A container is a virtual folder within a project which can contain content and other containers.\\

\par \textbf{Snapshot} \\
A snapshot is a read-only container from the state which the container the was in when the snapshot
was created.  A snapshot can not be updated and can only be deleted from the root of the snapshot.
Snapshots are by default stored as siblings to the container which they were made from, but they can
be contained by any container.\\

\par \textbf{File} \\
A file refers to an actual physical file. Files are stored in the database to make backup,
deployment and migration easier.\\

\par \textbf{User} \\
A user is the structure that handles people who have been granted access to the system. Access to
the system is handled by a separate service, like LDAP.\\

\subsubsection{Execution}
Java path finder was used to show that the model and plan of how to build the system was sound. The
model was built in Java with the objective of being as reduced and simple as possible, without
loosing any of the cases that needed to be covered by the model checker. As the users are mainly
going to be handled by external systems they were not included in the model.

@@

@@

\subsubsection{Front-end Refactorization}
The application could be made substantially more efficient by rewriting the front-end to update
itself according to the REST response after a modification of the project tree, instead of 
re-fetching the full project tree every time a change is made. The front-end should also be fixed to
properly follow the Reflux streamlining.
